State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

Using the same neural field basis function approximation, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving

@@

Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid. Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.

>>>>

Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving

@@

Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid. Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
